Unity in diversity: Children from 17 diverse communities process gaze in similar ways

### 2024-03-24 paper/paper.Rmd
update repo

---
title             : "A cross-cultural universal of human social cognition: Children from 17 diverse communities process gaze in similar ways"
shorttitle        : "Gaze-following across 17 communities"

>>>>

---
title             : "A universal of human social cognition: Children from 17 communities process gaze in similar ways"
shorttitle        : "Gaze-following across 17 communities"
